Open Source Capital Modeling Project
========================================================

This is an exploration of current open source tools available for building capital models for financial services companies.  This project started as a way to learn about best practices from the reproducible research movement in academia.  I wanted to learn how to leverage those techniques to build documentation and presentations using output from a capital model that could refresh automatically when a new model run was complete.  

That idea led to an option of either creating dummy data to test these techniques.  While starting down that rabbit hole, I decided to set back and try to Frankenstein together a very basic open source capital model that can be used publicly for training and presentations.  

The project is not intended to be even close to state of the art or scaleable for commercial use.

ESG
--------
Lets start by testing various ways to load in history to calibrate models.

```{r message=FALSE }
library(quantmod)
getSymbols("UNRATE",src="FRED") # US Unemployment rate rates from FRED
plot(UNRATE)

library(forecast)
plot(forecast(UNEMP))
library(FRBData)

GetInterestRates("TCMNOM", lastObs = 5) # get some data, treauries constant maturities/Nominal

library(Quandl)
Treasuries = Quandl("USTREASURY/YIELD", collapse="monthly", start_date="1970-01-01", type="ts")
plot(Treasuries[,7])
summary(Treasuries)

```

Fit basic CIR model to interest rates....

```{r }

```

Read in Sch P data from ISO Research Database found at:http://www.casact.org/research/index.cfm?fa=loss_reserves_data 

```{r}
# this is to read data

------------------Code Begin----------------------------------------------
a=read.csv(file.choose(),header=TRUE)

grp.code=unique(a$GRCODE)
grp.name=unique(a$GRNAME)
#
# function to get Schedule P triangle data given ins group
ins.line.data=function(g.code){
  b=subset(a,a$GRCODE==g.code)
  name=b$GRNAME
  grpcode=b$GRCODE
  ay=b$AccidentYear
  dev=b$DevelopmentLag

  cum_incloss=b[,6]
  cum_pdloss=b[,7]
  bulk_loss=b[,8]
  dir_premium=b[,9]
  ced_premium=b[,10]
  net_premium=b[,11]
  single=b[,12]
  posted_reserve97=b[,13]

  # get incremental paid losses - assume data is sorted by ay and dev
  inc_pdloss=numeric(0)
  for (i in unique(ay)){
    s=(ay==i)
    pl=c(0,cum_pdloss[s])
    ndev=length(pl)-1
    il=rep(0,ndev)
    for (j in 1:ndev){            
      il[j]=pl[j+1]-pl[j]
      }
    inc_pdloss=c(inc_pdloss,il)
    }
  data.out=data.frame(name,grpcode,ay,dev,net_premium,dir_premium,ced_premium,
     cum_pdloss,cum_incloss,bulk_loss,inc_pdloss,single,posted_reserve97)
  return(data.out)
  }
#


# Example

  comauto=ins.line.data(grp.code[1])

# upper triangle
com.insample=subset(comauto,ay+dev<=1998)
# lower triangle
com.outsample=subset(comauto,ay+dev>1998)
```

